Quantum-assisted unsupervised data clustering

### 2020-05-06 manuscript.tex
Fix measurement result dependence on ancila qubit #17

At this stage, the information regarding the differences between pairs of $\{X\}$ and $\{Y\}$ \hl{encoded in the amplitudes, in order to extract the Hamming distances between the relevant $\left| x_i \right\rangle$, $\left| y_j \right\rangle$ we return to our initial basis} for register $\left| X \right\rangle$ by applying pairwise CNOT gates:
%
\begin{multline}
    \left| \psi_f \right\rangle =  
    \frac{1}{\sqrt{kl}}\sum\limits_{i, j=1}^{k} 
	\left[ 
	    \cos\left(
	        \dfrac{\pi}{2n}
	        \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
	    \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+
        \left. i \sin\left(
            \dfrac{\pi}{2n}
            \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
        \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 1 \right\rangle
    \right] .
\end{multline}
%
This makes $\{X\}$ store the input vectors again, as in the initial step 
and preserves the amplitudes of the auxiliary qubit which are proportional to how different each pairs of $\{X\}$ and $\{Y\}$ are.

We thus have the Hamming distances encoded into the amplitudes of the final state. 
From the statistics of the measurement outcomes, the distance matrix between two data sets of binary vectors can be obtained (Fig.~\ref{fig:distance_matrix}). 
In this case, the biggest amplitude of the measurement result coincides with the smallest Hamming distance when the measurement result of the ancilla qubit is 0. 
If the ancilla qubit is 1, the smallest amplitude of the measurement result coincides with the smallest Hamming distance.

>>>>

At this stage, the information regarding the differences between pairs of $\{X\}$ and $\{Y\}$ \hl{encoded in the amplitudes, in order to extract the Hamming distances between the relevant $\left| x_i \right\rangle$, $\left| y_j \right\rangle$ we return to our initial basis} for register $\left| X \right\rangle$ by applying pairwise CNOT gates:
%
\begin{multline}
	\label{eq:final_state}
    \left| \psi_f \right\rangle =  
    \frac{1}{\sqrt{kl}}\sum\limits_{i, j=1}^{k} 
	\left[ 
	    \cos\left(
	        \dfrac{\pi}{2n}
	        \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
	    \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+
        \left. i \sin\left(
            \dfrac{\pi}{2n}
            \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
        \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 1 \right\rangle
    \right] .
\end{multline}
%
This makes $\{X\}$ store the input vectors again, as in the initial step 
and preserves the amplitudes of the auxiliary qubit which are proportional to how different each pairs of $\{X\}$ and $\{Y\}$ are.

From the statistics of the measurement outcomes of final state~(\ref{eq:final_state}) we recreate the amplitudes of ancilla qubit states. 
From those amplitudes estimations we are able to plot the distance matrix between two data sets of binary vectors.
The probability amplitude of the ancilla qubit outcomes captures the exact Hamming distance as the result of the preprocessing function.
There are two possible outcomes of measurement of the ancilla qubit, each has own probability amplitude and own interpretation of that amplitude. 
For instance, for the |0> outcome, the larger the amplitude the smaller the Hamming distance, 
and for the |1> outcome it is the other way around, magnitude of the amplitude of that outcome is proportional to the Hamming distance.
